GRASS: Distinguishing Planet-induced Doppler Signatures from Granulation with a Synthetic Spectra Generator

### 2022-08-30 src/tex/ms.tex
[showyourwork] overleaf sync

% \input{captions/fig1.tex}
\begin{figure*}[htb!]
\gridline{\fig{figures/fig1a.pdf}{0.4\textwidth}{}
          \fig{fig1b.pdf}{0.55\textwidth}{}}
\caption{Temporal and spatial variability in input bisectors encode turbulent granulation velocities. \textbf{Left:} To capture the line-of-sight variation observed in solar bisectors, observations were carried out at many discrete disk positions along each of the four solar limbs plus disk center. Figure adapted from Figure 1 of \citetalias{Lohner-Bottcher2018}. \textbf{Right:} Line bisectors differ in shape with both time and apparent position on the solar disk. From disk center ($\mu = 1$) to the limb ($\mu = 0$), bisectors transition from a distorted ``C"-shape to something more resembling a ``\textbackslash"-shape. This behavior results from the different viewing angles of convective granules along different lines of sight \citep[Figure 17.13 of ][]{Gray2008}. The solid, \revise{dashed, and dotted} lines trace the time-averaged bisector for each limb position. The shaded regions correspond to the $\pm1\sigma$ temporal variability of the bisectors at each limb position. Error bars in velocity are not shown; with an absolute wavelength calibration accuracy on order $\sim$$0.02$ m\AA\ ($\sim$1 $\ms$), the observed temporal variations are much larger than the typical uncertainty.}
\label{fig:one}
\script{fig1b.py}
\end{figure*}

@@

% \input{captions/fig2.tex}

>>>>

% \input{captions/fig1.tex}
\begin{figure*}[htb!]
\gridline{\fig{figures/fig1a.pdf}{0.4\textwidth}{}
          \fig{figures/fig1b.pdf}{0.55\textwidth}{}}
\caption{Temporal and spatial variability in input bisectors encode turbulent granulation velocities. \textbf{Left:} To capture the line-of-sight variation observed in solar bisectors, observations were carried out at many discrete disk positions along each of the four solar limbs plus disk center. Figure adapted from Figure 1 of \citetalias{Lohner-Bottcher2018}. \textbf{Right:} Line bisectors differ in shape with both time and apparent position on the solar disk. From disk center ($\mu = 1$) to the limb ($\mu = 0$), bisectors transition from a distorted ``C"-shape to something more resembling a ``\textbackslash"-shape. This behavior results from the different viewing angles of convective granules along different lines of sight \citep[Figure 17.13 of ][]{Gray2008}. The solid, \revise{dashed, and dotted} lines trace the time-averaged bisector for each limb position. The shaded regions correspond to the $\pm1\sigma$ temporal variability of the bisectors at each limb position. Error bars in velocity are not shown; with an absolute wavelength calibration accuracy on order $\sim$$0.02$ m\AA\ ($\sim$1 $\ms$), the observed temporal variations are much larger than the typical uncertainty.}
\label{fig:one}
\script{fig1.jl}
\end{figure*}

@@

% \input{captions/fig2.tex}
\begin{figure*}
    \epsscale{1.1}
    \plottwo{fig2a.pdf}{fig2b.pdf}
    \caption{Example pre-processed input data showing granular variability at disk center ($\mu = 1$). Each curve shows the input data at one snapshot in time. The color gradient has been added to aid the eye in separating out these realizations. \textbf{Left:} Line bisectors show variation due to pulsations and granulation. Changes in bisector shape encode granulation, and changes in position result from the combined effects of pulsations and granulation. Above continuum-normalized flux of 0.8 \revise{(gray hatched region)}, we model the bisector as the extrapolation from lower flux values. \textbf{Right:} Line widths measured as a function of depth show \revise{only slight} variation with time. These width measurements display significantly less \revise{temporal} variability compared to the line bisectors. Together, line bisectors and width as a function of depth uniquely specify the shape of a line at a given instance in time.}
    \label{fig:two}
    \script{fig2.jl}
\end{figure*}{}
